New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-08-10 paper/answer_rev_1.tex
wip

		First, thanks for dedicating your time to revise our work, it is a great honor for us to continue to improve our work with your help.

		Following we provide answers to each one of the comments you have given us:

@@

		We agree with that a real-world application connection was missing in our work. We believe that after the changes we made to address this issue, it is clear that the problems explored in our paper is not of limited interested.

		We address this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S. Canbolat and Michael von Massow. Planar maximal covering with ellipses.}", which covers with great detail the practical applications of the problems studied in our work:

@@

		This change can be found in page 3 of the manuscript. Also, to better fit this addition, we had to modify the paragraph after the added one; we do not display it here because it is not relevant to this comment.

@@

		Thanks for this idea of extension to our problem, we think it is very interesting, and we did devote some time to think about it.
		We believe that there is not a trivial adaptation to any of methods that would make it possible to work for this variation of the problem; at least for us it seems like it would require extensive work. 
		We added a paragraph to the conclusion to pass this idea on, giving it as a suggestion for future works on the subject:

>>>>

		First, thanks for dedicating your time to revise our work, it is a great honor for us to continue to improve our work with your help. We have split your review into two sections, which we called ``comments", one regarding the lack of a real-world application connection, and the other regarding potential extensions to the problems studied by us. Please find below our responses to them.
		\\

@@

		Thanks a lot for this great detailed feedback. 
		Upon receiving your input, we did question ourselves about the interest there is on our work, and we ended up coming to an agreement that a real-world connection is fundamental to making a case this problem is worth being published.
		We addressed this issue by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S. Canbolat and Michael von Massow. Planar maximal covering with ellipses.}", which covers with great detail the practical applications of the problems studied in our work:

@@

		This change can be found in page 3 of the manuscript. Also, to better fit this addition, we had to modify the paragraph after the added one; we do not display it here because it is not relevant to this comment.
		\\

@@

		Thanks for this idea of an extension to our problem, we think it is very interesting, and we did devote some time to think about it.
		We believe that there is not a trivial adaptation to any of our methods that would make it possible to work for this variation of the problem; at least for us, it seems like it would require extensive work. 
		We hypothesized that with this addition of a new variable (the ellipse's semi-major or semi-minor), we could have a similar result for MCER: there is a constant number of let's call locations (center, angle of rotation, and the new parameter), which makes four points be on the ellipse with a fixed area. Although, We could not prove it nor disprove it.
		We also thought about the possibility of having an optimization method on top of our current algorithm to decide the new parameter, but we could not think of a way we could make a model like that work.
		Even though we could not make too much out of the suggestion, we still believe that it could be a good idea for future works on the subject. Therefore, we added a paragraph to the conclusion to pass this idea on:
